New approaches to teachers' experience of stress: Do heart rate measurements with fitness trackers provide an efficient, inexpensive, and robust measurement method?

### 2024-08-02 02_paper/02_study/01_fitbit paper/Submission/FitBit_submission.Rmd

library(needs)
needs(ltm,
      broom,
      ppcor,
      jtools,
      lm.beta,
      tidyverse,
      janitor,
      lubridate,
      readxl,
      ggthemes,
      gridExtra,
      imputeTS,
      DescTools,
      cowplot,
      rstatix,
      ggpubr,
      lme4,
      viridis, 
      stargazer,
      papaja,
      grid)
```

@@

```{r}
df_regression <- 
  main_single_hr %>% 
  filter(time_span != "overall") %>%
  dplyr::select("ID", "time_span","time","heart_rate_std","heart_rate") %>% 
  distinct() %>% 
  mutate(time = time / 60) %>% 
  mutate(ID = as_factor(ID),
         Phase = factor(time_span,
                           levels = c("preparation","teaching","post","interview","end"),
                            labels = c("Pre Teaching Phase","Teaching Phase","Post Teaching Phase","Interview Phase","End Phase")
                           )
         )

@@

>>>>

library(needs)
needs(ltm,
      broom,
      ppcor,
      jtools,
      lm.beta,
      tidyverse,
      janitor,
      lubridate,
      readxl,
      ggthemes,
      gridExtra,
      imputeTS,
      DescTools,
      cowplot,
      rstatix,
      ggpubr,
      lme4,
      viridis, 
      stargazer,
      papaja,
      grid,
      purrr)
```

@@

```{r}
df_regression <- 
  main_single_hr |> 
  filter(time_span != "overall") |> 
  dplyr::select("ID",
                "time_span",
                "time",
                "heart_rate_std",
                "heart_rate") |> 
  distinct() |> 
  mutate(time = time / 60) |> 
  mutate(ID = as_factor(ID),
         Phase = factor(time_span,
                        levels = c("preparation",
                                   "teaching",
                                   "post",
                                   "interview",
                                   "end"),
                        labels = c("Pre Teaching Phase",
                                   "Teaching Phase",
                                   "Post Teaching Phase",
                                   "Interview Phase",
                                   "End Phase")
                           )
         )

@@

table_data$n[table_data$Phase == "Pre Teaching Phase"] <- df_regression %>% filter(Phase == "Pre Teaching Phase") %>% pull(heart_rate_std) %>% length()
table_data$n[table_data$Phase == "Teaching Phase"] <- df_regression %>% filter(Phase == "Teaching Phase") %>% pull(heart_rate_std) %>% length()
table_data$n[table_data$Phase == "Post Teaching Phase"] <- df_regression %>% filter(Phase == "Post Teaching Phase") %>% pull(heart_rate_std) %>% length()
table_data$n[table_data$Phase == "Interview Phase"] <- df_regression %>% filter(Phase == "Interview Phase") %>% pull(heart_rate_std) %>% length()
table_data$n[table_data$Phase == "End Phase"] <- df_regression %>% filter(Phase == "End Phase") %>% pull(heart_rate_std) %>% length()

tab_2 <- apa_table(table_data,
                   placement = 'h',
                   label = 'tab_2',
                   caption = 'Descriptive statistics (n, M, SD) for the mean intercepts and the mean slopes for the five intervals',
                   note = 'Please note that M and SD of the overall course vs. the individual intervals were not exactly 0 and 1 due to rounding differences.' 
                   )

writeLines(tab_2, 'tab_2.tex')

```{=latex}
\input{tab_2.tex}
```

### 2024-08-02 02_paper/02_study/01_fitbit paper/Submission/tab_1.tex

\caption{\label{tab:table_1}Mean HR (M), standard deviations HR (SD), and range of teachers’ HR over the course of the entire study and the five intervals (unstandardized in BPM/z-standardized)}

\begin{tabular}{lllll}
\toprule
Interval & \multicolumn{1}{c}{M HR} & \multicolumn{1}{c}{SD HR} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max}\\
\midrule
Overall Course of 2h & 90.09/-0.04 & 15.76/0.99 & 51/-4.03 & 164/4.56\\
Pre-teaching interval & 77.95/-1.07 & 11.14/0.57 & 50/-2.68 & 120/2.96\\
Teaching interval & 82.32/-0.72 & 11.85/0.74 & 51/-2.51 & 132/4.39\\
Post-teaching interval & 93.61/0.27 & 14.01/0.76 & 60/-2.17 & 150/3.06\\
Interview interval & 96.28/0.48 & 14.11/0.88 & 56/-3.56 & 139/3.24\\
End Interval & 100.8/0.85 & 16.23/0.77 & 63/-2.18 & 164/4.37\\
\bottomrule
\addlinespace
\end{tabular}

>>>>

\caption{Mean HR (M), standard deviations HR (SD), and range of teachers’ HR over the course of the entire study and the five intervals (unstandardized in BPM/z-standardized)}

\begin{tabular}{lllll}
\toprule
Interval & \multicolumn{1}{c}{M HR} & \multicolumn{1}{c}{SD HR} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max}\\
\midrule
Overall Course of 2h & 90.09/-0.04 & 15.76/0.99 & 51/-4.03 & 164/4.56\\
Pre-teaching interval & 77.95/-1.07 & 11.14/0.57 & 50/-2.68 & 120/2.96\\
Teaching interval & 82.32/-0.72 & 11.85/0.74 & 51/-2.51 & 132/4.39\\
Post-teaching interval & 93.61/0.27 & 14.02/0.76 & 60/-2.17 & 150/3.06\\
Interview interval & 96.28/0.48 & 14.11/0.88 & 56/-3.56 & 139/3.24\\
End Interval & 100.8/0.85 & 16.24/0.77 & 63/-2.18 & 164/4.37\\
\bottomrule
\addlinespace
\end{tabular}
